### 2016-01-21 AcademicPaperSummaries/PaperSummaries.tex
Aksoy and Carter from PE Terrorism Week Three

Structure:
Citation
Research question and research area
Summary of argument and mechanism
Data \& methods
Findings
Notes on related papers

@@

This is a literature review essay about the then-current strand of the literature of academic study of terrorism, with a particular focus on the outcomes of formal models.

>>>>

Keywords provide a shorthand for broad type of paper (theory development, disaggregation, test theory, introduce data., literature review....); empirical approach (formal model, quant, computational)
Structure:
Citation
Research question and research area
Summary of argument and mechanism
Data \& methods
Findings
Notes on related papers

@@

Key: literature review.

This is a literature review essay about the then-current strand of the literature of academic study of terrorism, with a particular focus on the outcomes of formal models.  There is not a theory that is being tested, so there isn't data to assess. Note that, as with all EBdM papers about terrorism, he presents the results of his own research as if the conclusions are settled questions in the field.

\textbf{Aksoy, Deniz and David B. Carter. 2014. “Electoral Institutions and the Emergence of Terrorist Groups.” British Journal of Political Science 44(1): 181-204.}

Key: disaggregation; quant.

Research question and area: Aksoy and Carter build on the literature about how domestic institutions-- and particularly democratic institutions-- influence the emergence of terror groups. They are in the `` do democracies experience more terrorism'' research agenda. A\&C look at how different types of terror groups (``within-system'' who have goals that can be fulfilled within existing system and ``anti-system'' whose goals require complete overthrow of the existing political system. Irredentist and separatist groups are called anti-system.) are differently influenced by democratic institutions, and argue that previous research hasn't found ``robust'' evidence of a connection between electoral rules and terrorism because it combines all groups together. Thus, this is a \underline{disaggregation} type paper.
Articulated/assumed definition of ``terrorism'': Terrorism is a political organization trying to ``achieve their goals by using violence against civilians''
Summary of argument and mechanism: Democratic institutions should reduce operation of within-system groups because they provide a way for the goals of the organization to be met; should not have an impact on anti-system groups.
Data \& methods: Look only at domestic groups; data is from Jones and Libick (2006), which has 648 terror grops from 1968-2006, and TWEED, which has 286 groups from 150-2004. Three main DVs: emergence of any group, emergence of anti-system group, emergence of within-system group. Unit of analysis is country-year. Primary IDVs: indicator variable for democracy, domestic institutions from IAEP and Democratic Electoral Systems Around the World Project, log of district magnitude, and various controls. Model is logit.
Findings: permissive electoral systems associated with reduced risk of within-system group emergence but have no impact on anti-system groups. 
Notes on related papers:
